### 2019-10-21 README.Rmd
Spell check README and vignette

In 2012 KEGG released its first application programming interface (API), and has been
adding features and functionality ever since. There are benefits to using an API.
First, API's like KEGG's allow users to perform customized analyses with the most
up-to-date versions of the data contained in the database. In addition, accessing the
KEGG API is very easy using statistical programming tools like R or Python and
integrating data retrevial into user's code makes the program reproducible. To 
further enforce reproducibilty *diffEnrich* adds a date and KEGG release tag to
all data files it generates from accessing the API. For update histories and release 
notes for the KEGG REST API please go [here](https://www.kegg.jp/kegg/rest/).

@@

**Note:** Because it is assumed that the user might want to use the data sets generated by *get_kegg*, it is careful not to
overwrite data sets with exact names. *get_kegg* checks the path provided for data sets generated 'same-day/same-version', 
and if it finds even one of the three, it will not re-write any of the data sets. It will still however, let the user know
it is not writing out new data sets and still generate the named list object. Users can generate 'same-day/same-version'
data sets in different directories if they so choose. Additionaly, *get_kegg* can be used to read in saved versions of the txt files
generated from a previous call (like those displayed above), and generate an R list object that is compatible with downstream
functions.

@@

Shearn CT. et al. (2019) Cholestatic liver disease results increased production of reactive aldehydes and an atypical periportal hepatic antioxidant response. Free Radic Biol Med;143:101-114. [Epub ahead ofbprint] PubMed PMID: 31377417.

>>>>

In 2012 KEGG released its first application programming interface (API), and has been
adding features and functionality ever since. There are benefits to using an API.
First, API's like KEGG's allow users to perform customized analyses with the most
up-to-date versions of the data contained in the database. In addition, accessing the
KEGG API is very easy using statistical programming tools like R or Python and
integrating data retrieval into user's code makes the program reproducible. To 
further enforce reproducibilty *diffEnrich* adds a date and KEGG release tag to
all data files it generates from accessing the API. For update histories and release 
notes for the KEGG REST API please go [here](https://www.kegg.jp/kegg/rest/).

@@

**Note:** Because it is assumed that the user might want to use the data sets generated by *get_kegg*, it is careful not to
overwrite data sets with exact names. *get_kegg* checks the path provided for data sets generated 'same-day/same-version', 
and if it finds even one of the three, it will not re-write any of the data sets. It will still however, let the user know
it is not writing out new data sets and still generate the named list object. Users can generate 'same-day/same-version'
data sets in different directories if they so choose. Additionally, *get_kegg* can be used to read in saved versions of the txt files
generated from a previous call (like those displayed above), and generate an R list object that is compatible with downstream
functions.

@@

Shearn CT. et al. (2019) Cholestatic liver disease results increased production of reactive aldehydes and an atypical periportal hepatic antioxidant response. Free Radic Biol Med;143:101-114. [Epub ahead of print] PubMed PMID: 31377417.
